Vowel Elision in Yoruba Collocations

### 2023-02-26 paper.tex
Description of algorithm sorta complete

We are now in the appropriate setting to identify the correct output form.
In order to do this, we must evaluate our entire set of constraints against
all of the 65536 candidate surface forms we generated previously. This will
generate a sequence of constraint violations, one for each candidate surface
form.

@@

@@

>>>>

We are now in the appropriate setting to identify the correct output form. In
order to do this, we must evaluate our entire set of constraints against all of
the 65536 candidate surface forms we generated previously. This will generate a
sequence of constraint violations, one for each candidate surface form. We
search through each sequence in parallel, looking at the number of violations
for each constraint at the same time, starting from the highest-ranked. We
determine the minimal number of violations for the current constraint, and
eliminate all candidates with violation counts that exceed this threshold. We
repeat until we have a single candidate left, and return this candidate.

TODO: describe the algorithm succinctly using an algorithm figure?

@@

TODO: Figure out how best to implement the algorithm described above.

TODO: Show code examples of the critical parts, one for each of the
subsections above!

@@

In this section we will evaluate all of our collected Yoruba underlying
representations against the expected surface forms.

TODO: Requires implementation to be reasonably far along first!
